%-------------------------
% Resume in Latex
% Author : Anush Ramesh
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{charter}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins to ensure the name is fully visible and not cut off
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.3in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Anush Ramesh} \\ \vspace{3pt}
    {\small \textbf{AI/ML \hspace{2pt}\textbar\hspace{2pt} Computer Vision \hspace{2pt}\textbar\hspace{2pt} Data Science}} \\ \vspace{3pt}
    \small 6290228918 $|$ \href{mailto:anushramesh2023@gmail.com}{anushramesh2023@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/anushramesh07}{LinkedIn} $|$
    \href{https://github.com/CoderAnush}{GitHub} $|$
    \href{https://anushramesh.netlify.app}{Portfolio}
\end{center}
\vspace{-15pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Amrita Vishwa Vidyapeetham}{Coimbatore, Tamil Nadu}
      {Bachelor of Technology in Electrical and Computer Engineering}{Aug. 2023 -- April 2027}
  \resumeSubHeadingListEnd
\vspace{-5pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI/ML Intern}{June 2025 -- July 2025}
      {Edunet Foundation}{Remote}
      \resumeItemListStart
        \resumeItem{Completed a 4-week AICTE Microsoft internship focused on AI, ML, and Azure Cloud.}
        \resumeItem{Built a supervised ML model in Python for cricket match outcome prediction using data preprocessing, feature engineering, and model evaluation.}
      \resumeItemListEnd

    \resumeSubheading
      {AI \& Edge Computing Intern}{June 2026}
      {Larsen \& Toubro}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Developed an AI-based Biomedical Waste Segregation Monitoring System for automated biomedical waste classification using Computer Vision techniques.}
        \resumeItem{Built and annotated a biomedical waste dataset comprising 9,124 images across 8 waste categories using Roboflow.}
        \resumeItem{Trained, tested, and evaluated a custom YOLOv11 Nano object detection model for biomedical waste detection and performance validation.}
        \resumeItem{Presented project methodology, implementation, and results to industry mentors.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-5pt}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
          {\textbf{Biomedical Waste Segregation Monitoring System} $|$ \emph{Python, YOLOv11, OpenCV, Streamlit, Power BI}}{}
          \resumeItemListStart
            \resumeItem{Developed an end-to-end Computer Vision and Object Detection system for automated biomedical waste classification and disposal-bin recommendation.}
            \resumeItem{Built and annotated a dataset of 9,124 images across 8 biomedical waste classes using Roboflow.}
            \resumeItem{Achieved 95.5\% mAP@50, 91.4\% Precision, and 95.4\% Recall through training and evaluation of a custom object detection model.}
            \resumeItem{Developed Streamlit and Power BI dashboards for real-time monitoring, reporting, and waste analytics.}
          \resumeItemListEnd
          \small{\href{https://github.com/CoderAnush/AI-BASED-MEDICAL-WASTE-SEGREGATION-MONITORING-SYSTEM-FOR-MULTI-SPECIALITY-HOSPITALS}{\textit{GitHub Link} - Biomedical Waste Segregation Project}} \vspace{2pt}

      \resumeProjectHeading
          {\textbf{RepoMind — AI-powered Code Analysis \& Search Platform} $|$ \emph{Python, LangGraph, Qdrant Cloud, FastAPI, PostgreSQL, React Flow}}{}
          \resumeItemListStart
            \resumeItem{Developed a semantic search engine (RAG) using LangGraph and Qdrant Cloud for interactive codebase Q\&A with source citations.}
            \resumeItem{Constructed a Graph Database parser to automatically map and visualize complex multi-file repository architecture relationships.}
            \resumeItem{Built security auditing pipeline scanning repositories with line-by-line recommendation logs.}
            \resumeItem{Integrated secure GitHub OAuth and background workers for seamless codebase imports.}
          \resumeItemListEnd
          \small{\href{https://github.com/CoderAnush/RepoMind}{\textit{GitHub Link} - RepoMind Project}} \vspace{2pt}

      \resumeProjectHeading
          {\textbf{AI-Based Gas \& Smoke Early Warning System} $|$ \emph{Python, Random Forest, STM32, UART, Actuators}}{}
          \resumeItemListStart
            \resumeItem{Engineered an Edge ML early warning system utilizing a trained Random Forest classifier.}
            \resumeItem{Collected and processed a dataset of 28,000+ gas sensor readings for model training.}
            \resumeItem{Configured bidirectional UART communication between PC inference service and STM32 microcontroller.}
            \resumeItem{Deployed hardware actuators (exhaust fans, alarms) triggered automatically by UART inference signals.}
          \resumeItemListEnd
          \small{\href{https://github.com/CoderAnush/OPENLAB-PROJECT}{\textit{GitHub Link} - Gas \& Smoke Early Warning Project}} \vspace{2pt}

      \resumeProjectHeading
          {\textbf{Live Sign Language Transcription System} $|$ \emph{Python, TensorFlow, OpenCV, RNN, LSTM}}{}
          \resumeItemListStart
            \resumeItem{Developed a real-time American Sign Language (ASL) transcription system using deep learning techniques.}
            \resumeItem{Designed an RNN-LSTM architecture for sequential gesture recognition and real-time text generation.}
            \resumeItem{Implemented OpenCV-based gesture capture and preprocessing pipelines for live inference.}
          \resumeItemListEnd
          \small{\href{https://github.com/CoderAnush/LIVE-SIGN-LANGUAGE-TRANSCRIPT}{\textit{GitHub Link} - Sign Language Transcription Project}} \vspace{2pt}

    \resumeSubHeadingListEnd
\vspace{-5pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages:} Python, C/C++, SQL \\
     \textbf{Machine Learning \& Deep Learning:} Scikit-Learn, TensorFlow, Keras, PyTorch, Deep Learning, Model Evaluation \\
     \textbf{Computer Vision:} OpenCV, YOLOv11, Object Detection, Image Classification, Dataset Annotation, Data Augmentation \\
     \textbf{Data Analysis \& Visualization:} Pandas, NumPy, Matplotlib, Power BI, Exploratory Data Analysis (EDA) \\
     \textbf{AI Frameworks \& Agentic AI:} LangChain, LangGraph, Agentic AI, RAG, Vector Databases \\
     \textbf{Embedded Systems \& IoT:} STM32, ESP32, Arduino, Raspberry Pi Pico, UART Communication, MQTT Protocols, Hardware Actuators \\
     \textbf{Development \& Deployment:} Streamlit, FastAPI, Git, GitHub, Roboflow, Vercel, Render
    }}
 \end{itemize}

\end{document}
